\begin{center}
    \chapter*{Bibliography}
    \addcontentsline{toc}{chapter}{Bibliography}
\end{center}

\noindent
\hangindent=1.5em [1] P. Kulurkar et al., \textit{IoT-Enabled Fall Detection Using LSTM and Edge Computing}, [Journal/Conference Name], 2023.

\hangindent=1.5em [2] M. E. Karar, H. I. Shehata, and O. Reyad, \textit{Comprehensive Survey of IoT-Based Fall Detection Systems}, [Journal/Conference Name], 2022.

\hangindent=1.5em [3] H. Jin, W. Zhou, and Y.-C. Lin, \textit{Augmented Reality and Visual AI for Fall Detection}, [Journal/Conference Name], 2024.

\hangindent=1.5em [4] O. Z. Salah, S. K. Selvaperumal, and R. Abdulla, \textit{Accelerometer-Based Elderly Fall Detection System Using Edge Artificial Intelligence Architecture}, in [Book Title]. [Publisher Location]: Publisher, 2022.

\hangindent=1.5em [5] X. Wang, J. Ellul, and G. Azzopardi, \textit{Elderly Fall Detection Systems}, [Journal/Conference Name], 2020.

\hangindent=1.5em [6] Z. Mohammad, A. R. Anwary, M. F. Mridha, M. S. H. Shovon, and M. Vassallo, \textit{An Enhanced Ensemble Deep Neural Network Approach for Elderly Fall Detection System Based on Wearable Sensors}, [Journal/Conference Name], 2023.

\hangindent=1.5em [7] A. Ibrahim, K. Chaccour, G. Badr, and A. H. El Hassani, \textit{Fall Detection Algorithm using Body Angle for Accurate Classification of Falls and ADLs}, [Journal/Conference Name], 2021.

\hangindent=1.5em [8] P. Chutimawattanakul and P. Samanpiboon, \textit{Fall Detection for the Elderly using YOLOv4 and LSTM}, [Journal/Conference Name], 2022.

\hangindent=1.5em [9] S. Badgujar and A. S. Pillai, \textit{Fall Detection for Elderly People Using Machine Learning}, [Journal/Conference Name], 2020.

\hangindent=1.5em [10] L. Shabadi et al., \textit{Real-Time Elderly Fall Detection as Ambient Intelligence in Old Age Homes}, [Journal/Conference Name], 2025.

\hangindent=1.5em [11] X. Lv, Z. Gao, C. Yuan, M. Li, and C. Chen, \textit{Hybrid Real-Time Fall Detection System Based on Deep Learning and Multi-Sensor Fusion}, [Journal/Conference Name], 2020.

\hangindent=1.5em [12] R. Vyas, J. A. Shirley, and R. Jansi, \textit{Fall Detection System for Elderly People Using Piezoresistive Textile Pressure Sensor}, [Journal/Conference Name], 2025.

\hangindent=1.5em [13] [Authors Not Specified], \textit{IoT-Based Fall Detection Monitoring and Alarm System for Elderly}, [Journal/Conference Name], [Year, if available].

\hangindent=1.5em [14] T. Imamura, V. G. Moshnyaga, and K. Hashimoto, \textit{Automatic Fall Detection by Using Doppler-Radar and LSTM-Based Recurrent Neural Network}, [Journal/Conference Name], 2022.

\hangindent=1.5em [15] S. Lahouar, M. Mansour, and M. H. Said, \textit{Development of a Fall Detection System Based on a Tri-Axial Accelerometer}, [Journal/Conference Name], [Year, if available].
